An Improved ANS Transaction Template

### 2018-01-26 paper.tex
done with the experiement description

\subsubsection{Case 2}
The case 2 is design is also limited to 30 cascades in the scenario (limit of
the JCPOA agreement), but this time each level of cascade are designed to get
feed with the previous level product and to have 4 stripping stages and 10
enriching stages. The configuration of the different level of cascade can be
found in table \ref{}
\begin{table}[htb]
\centering
\begin{tabular}{lllll}
\toprule

@@

\bottomrule
\end{tabular}
  \caption{Summary of the different properties of the different level of cascade.}
  \label{tab:widetable}
\end{table}

>>>>

\subsubsection{Case 2}
The case 2 is design is also limited to 30 cascades in the scenario (limit of
the JCPOA agreement), but this time each level of cascade are designed to get
feed with the previous level product and to have 4 stripping stages and 10
enriching stages. The configuration of the different level of cascade can be
found in table \ref{tab:cascadelvl}. The different cascades don't have the same
geometry: the number of centrifuges per stage depends on their own design and
varies slightly from a level to another.

\begin{table}[htb]
\centering
\begin{tabular}{lllll}
\toprule

@@

\bottomrule
\end{tabular}
  \caption{Summary of the different properties of the different level of cascade.}
  \label{tab:cascadelvl}
\end{table}
